---
title: "Assignment 1"
author: "Rushabh Barbhaya"
date: "4/2/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis Of Variance

Exploring the data

```{r}
library(moments)
data = read.csv("EspressoData.csv")
head(data)
str(data)
summary(data)

plot(density(data$cereme))
qqnorm(data$cereme)
```
## Skewness Test

$H_0:$ There is no skewness \
$H_A:$ There is skewness in the data \
The p-value is greater than 0.1. $\therefore$ we cannot accept the null hypothesis \

```{r}
agostino.test(data$cereme)
```

## Normality Test

$H_0:$ The data is normally distributed \
$H_A:$ The data is not normally distributed \
p-value is less than 0.05. $\therefore$ we cannot reject the null hypothesis \

```{r}
shapiro.test(data$cereme)
```

performing log correction plotting density and residual plots \

```{r}
data$cereme2 = log(data$cereme)
plot(density(data$cereme2))
qqnorm(data$cereme2)

agostino.test(data$cereme2)
shapiro.test(data$cereme2)

eruption.lm = lm(cereme2 ~ brewmethod, data = data)
summary(eruption.lm)
eruption.res = resid(eruption.lm)
summary(eruption.res)
plot(data$cereme2, eruption.res, ylab = "Residuals", xlab = "Brew Method", main = "data brewing method")
abline(0,0)
```

## Variance Test

$H_0:$ The variance in each group is the same \
$H_A:$ The variance in each group is not the same \
p-value is greater than 0.1. $\therefore$ we cannot accept the hypothesis \

```{r}
bartlett.test(data$cereme2, data$brewmethod)
tapply(data$cereme2, data$brewmethod, var)
```

## ANOVA
```{r}
summary(aov(cereme2 ~ factor(brewmethod), data = data))
model2 <- aov(cereme2 ~ factor(brewmethod), data = data)
summary(model2)
```

## Post hoc test

For pairwise test, brew method 2-3 is different from other \
Brew method 2 has a lot of variance as compared to others \
The effect for method 2 is too large \

```{r}
pairwise.t.test(data$cereme2, data$brewmethod, paired = FALSE, p.adjust.method = "bonferroni")

library(pgirmess)
kruskalmc(data$cereme2, factor(data$brewmethod), data = data)
TukeyHSD(model2)

library(compute.es)
library(pastecs)
by(data$cereme2, data$brewmethod, stat.desc)

mes(3.45254057, 4.10322338, 0.24759907, 0.16980514, 9, 9)
mes(3.66650368, 4.10322338, 0.17750446, 0.16980514, 9, 9)
```

