---
title: "Assignment 2 - ANOVA - Blocking"
author: "Rushabh Barbhaya"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
1. What assumption must we test to include a variable as a blocking factor?
    + Kurtosis, Skewness, Normality, Independence of Observation, Variance test, and Additivity
    + Blocking technique should also help us reduce the Error
    
2. Recognize the IV, DV, block and create a table for the following research statement.
    + Independent Variable: Motor Skill Test (condition)
    + Dependent Variable: Performance Score (Performance_score)
    + Blocking Variable: Age Group (Age)
\
\

```{r Table, warning=FALSE, echo=FALSE}
library(knitr)
table_fit = matrix(NA, nrow = 3, ncol = 2)
table_fit[1,] = c("Variable", "#Levels")
table_fit[2,] = c("Motor Skill Test", "3")
table_fit[3,] = c("Age(Block)", "3")
kable(table_fit, caption = "Specification Table", format = "pipe")

mat_fit = matrix(NA, nrow = 4, ncol = 4)
mat_fit[1,] = c("", "Test1", "Test2", "Test3")
mat_fit[2,] = c("Age_60-69", "", "", "")
mat_fit[3,] = c("Age_70_79", "", "", "")
mat_fit[4,] = c("Age_80+", "", "", "")
kable(mat_fit)
```

## ANOVA
#### Hypothesis

$H_0:$ Performance Scores of all elderly people are equal \
$H_A:$ Performance Scores of all elderly people may not be equal  \
    
#### Assumptions
- From the density plot, there seems to have 2 spikes which may affect our results 
- We fail to reject the null hypothesis on kurtosis test 
- We fail to reject the null hypothesis from skewness test 
- We fail to reject the null hypothesis in normality test 
- We fail to reject the null hypothesis for variance test 
- The largest to smallest ratio of variance is less than 3. Which is not enough evidence to reject the null hypothesis 
- Model1 --> Condition*Age, is not a significant factor 
- Model2 --> Condition, is a significant factor 
- Model3 --> Age, is a significant factor 
- Model4 --> Condition+Age, is cannot be a blocker, it's a significant factor
- Condition1 --> n = 28, Mean = 32.0714286, SD = 4.2854497
- Condition2 --> n = 30, Mean = 27.8666667, SD = 4.5768031
- Condition3 --> n = 31, Mean = 23.0645161, SD = 4.5529147
\

#### Summary

\
```{r assignment, results='hold', warning=FALSE}
library(readxl)
library(moments)
library(pgirmess)
library(pastecs)
library(compute.es)

data <- read_excel("Lab3.xlsx")
summary(data)

# Denisty Plot
plot(density(data$Performance_score))
qqnorm(data$Performance_score)

# Kurtosis Test
anscombe.test(data$Performance_score)

# Skewness Test
agostino.test(data$Performance_score)

# Normality Test
shapiro.test(data$Performance_score)

#Residual Plot
perf.lm = lm(Performance_score ~ Condition, data = data)
perf.res = resid(perf.lm)
plot(data$Performance_score, perf.res, ylab = "Residual", xlab = "Condition", main = "Independence of Observation")
abline(0, 0)

# Variance Test
bartlett.test(data$Performance_score, data$Condition)
tapply(data$Performance_score, data$Condition, var)

# ANOVA with Blocking
model1 = aov(Performance_score ~ factor(Condition)*factor(Age), data = data)
summary(model1)
model2 = aov(Performance_score ~ factor(Condition), data = data)
summary(model2)
model3 = aov(Performance_score ~ factor(Age), data = data)
summary(model3)
model4 = aov(Performance_score ~ factor(Condition)+factor(Age), data = data)
summary(model4)

anova(model1, model2)

#Pairwise t test
pairwise.t.test(data$Performance_score, data$Condition, paired = FALSE, p.adjust.method = "bonferroni")

#Tukey's test
TukeyHSD(model1)

by(data$Performance_score, data$Condition, stat.desc)
mes(27.8666667, 32.0714286, 4.5768031, 4.2854497, 30, 28)
mes(23.0645161, 27.8666667, 4.5529147, 4.5768031, 31, 30)
mes(23.0645161, 32.0714286, 4.5529147, 4.2854497, 31, 28)
```

